---
title: "D3ManhattanPlot Demo"
author: "Nick Strayer"
date: "August 1, 2015"
output:
  html_document:
    fig_width: 9
---
### Intro: 
This is a simple use case of using the D3ManhattanPlots HTMLWidget for R to generate interactive manhattan plots for genome wide association studies (GWAS). 
The package/widget are on [github](http://github.com/nstrayer/D3ManhattanPlots) where you are encuraged to submit issues for desired features (or pull requests for the more adventurous).

### What is this plot?
Each balloon and string represents a single snp, or base pair on the genome. The height of the bar represents its significance of correlation with a trait or phenotype. These data are a subsection (100 most significant snps when stratified by the male gender) of the data from [Complement factor H polymorphism in age-related macular degeneration. Klein et al. 2005](http://www.ncbi.nlm.nih.gov/pubmed/15761122). 

### How to use: 
First we load the library and data: 
```{r}
library(manhattanPlot)
d = sampleVals
```

Take a quick peak at the data: 
```{r}
head(d)
```

...and plot: 
```{r}
manhattanPlot(d)
```

### Some more examples: 

If we want to see it with slightly less homogeneous data we can use an included randomly generated dataset.

```{r}
manhattanPlot(random)
```

We can also play around with some of the options. 

```{r}
manhattanPlot(random, sigLine = FALSE, animationSpeed = 0)
```

